SoK: Web Application Attack Defenses (in Question)

### 2014-10-12 docs/questioning.tex
minor change
initial figure with the attack model(s)

Application attacks that involve {\sc dsl}s,
constitute an important subset of the code injection problem,
as {\sc dsl}s like {\sc sql} and {\sc xml} play an
significant role in the development of either web or mobile
applications. For example, many applications have interfaces
where a user enters input to interact with the
application's data, thereby interacting with the
underlying {\it Relational Database Management System}
({\sc rdbms}).
This input can become part of an
{\sc sql} query and executed on the target {\sc rdbms}.
A code injection attack that exploits the vulnerabilities of these
interfaces by taking advantage of input validation issues like
incorrectly passed parameters or incorrect type handling,
is called an ``{\sc sql} injection
attack''~\cite{CERT02,MS09,HVO06,SW06}.
By using similar techniques malicious users
can perform other exploits based on {\sc dsl}s,
like {\sc xp}ath~\cite{SW06,CDL07,MKS09} and
{\sc xml}~\cite{MSM13} injection attacks.

@@

@@

	\multirow{8}{*}{Runtime Tainting}

@@

  \multirow{10}{*}{Training}

>>>>

Application attacks that involve {\sc dsl}s,
constitute an important subset of the code injection problem,
as {\sc dsl}s like {\sc sql} and {\sc xml} play an
significant role in the development of either web or mobile
applications. For example, many applications have interfaces
where a user enters input to interact with the
application's data, thereby interacting with the
underlying {\it Relational Database Management System}
({\sc rdbms}).
This input can become part of an
{\sc sql} query and executed on the target {\sc rdbms}.
A code injection attack that exploits the vulnerabilities of these
interfaces by taking advantage of input validation issues like
incorrectly passed parameters or incorrect type handling,
is called an ``{\sc sql} injection
attack''~\cite{CERT02,MS09,HVO06,SW06}.
By using similar techniques malicious users
can perform other exploits based on {\sc dsl}s,
like {\sc xp}ath~\cite{SW06,CDL07,MKS09} and
{\sc xml}~\cite{MSM13}.

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.57]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:taxonomy}Attack model demonstrating web
application attacks that involve code injection.}
\end{figure*}

@@

	\multirow{9}{*}{Runtime Tainting}

@@

  \multirow{9}{*}{Training}
